---
title: "Actividad 1"
author: "Pilar Piñeiro"
date: "21 de abril de 2016"
output: html_document
---

#Teorema central del límite
##Actividad 1

###**Objetivo de la actividad: Análisis del teorema central del límite**###



####Intro####


If we take repeated samples from the same population under study and calculate their corresponding sample means, the distribution of this sample mean will approach a normal distribution in the limit case (when n tends to infinity). This property is what is known as the central limit theorem.
 
####Procedure####


I'm going to take 50 samples of sample size n = 5, n = 25, n = 100 and n = 2000
using *runif()* following a uniform distribution. Next, I will calculate the mean of each of the matrices created:

```{r echo=TRUE}
#Create matrix
n5<-matrix(runif(5),nrow=50)
n25<-matrix(runif(25),nrow=50)
n100<-matrix(runif(100),nrow=50)
n2000<-matrix(runif(2000),nrow=50)

#Create matrix list
MatrixList<-list(n5,n25,n100,n2000)

#Apply mean:
MatrixList.means<-lapply(MatrixList,rowMeans)
```

The plots below show the results of the distribution of the means based on the sample size.

It can be seen that with the smallest sample size, the calculated means do not show a tendency to a normal distribution. When the sample size is larger, a normal pattern begins to appear. With a sample size of 2000, the normal distribution is clearly seen.


```{r}
 #4 subplots
 par(mfrow=c(2,2))
 
 #Histograms
 hist(MatrixList.means[[1]],xlim=range(0:1),main="n=5",xlab="")
hist(MatrixList.means[[2]],xlim=range(0:1),main="n=25",xlab="")
 hist(MatrixList.means[[3]],xlim=range(0:1),main="n=100",xlab="")
hist(MatrixList.means[[4]],xlim=range(0:1),main="n=2000",xlab="") 
 

```

It is observable that the extent of the data decreases as the sample size increases.

This is because the measure of variation (the standard deviation, or standard error of the mean) is inversely proportional to the square root of the sample size: if you want to increase the precision of the sample mean, an increase of the size of said sample will always influence.

* Bibliography: Seefeld K and Linder E. Statistics Using R with Biological Examples *